Points Above Replacement: A New NBA Metric to Evaluate Player Performance

### 2022-04-26 Manuscript/Manuscript.tex
Add files via upload

Creating the ``Team Adjustment'' statistic via 
equation~\ref{eq:TeamAdjustment} has then successfully adjusted a 
player's statistics to his specific team.

@@

By creating the ``Points Per Win'' statistic, equation~\ref{eq:PointsPerWin} 
has thus scaled down the statistic based 
on how many points are in an average win, similar to Runs Per Win in 
WAR. The constant of 2,160 would change to 2,460 for an 82-game 
season, for a typical NBA season.

@@

Equation~\ref{eq:PAR} gives a good idea of how many points a player 
accounts for 
during a 
game, how important that is for 
his given team, and how important it is compared to all other players. The 
last step is to standardize this 
 rough PAR statistic, so that the mean is 0, and the standard deviation is 
1. 
Logically, this helps the idea of the 
metric in the sense that a perfectly league average player should have a 
PAR of 0, and his presence or 
absence from his team neither adds nor subtracts value. Thus, we have 
created a new NBA player metric, 
Points Above Replacement, PAR. All of the calculations, multiple 
regression, and graphs were created using R \citep{R}.

>>>>

Creating the ``Team Adjustment'' statistic via 
Equation~\eqref{eq:TeamAdjustment} has then successfully adjusted a 
player's statistics to his specific team.

@@

By creating the ``Points Per Win'' statistic, Equation~\eqref{eq:PointsPerWin} 
has thus scaled down the statistic based 
on how many points are in an average win, similar to Runs Per Win in 
WAR. The constant of 2,160 would change to 2,460 for an 82-game 
season, for a typical NBA season.

@@

Equation~\eqref{eq:PAR} gives a good idea of how many points a player 
accounts for 
during a 
game, how important that is for 
his given team, and how important it is compared to all other players. The 
last step is to standardize this 
 rough PAR statistic, so that the mean is 0, and the standard deviation is 
1. 
Logically, this helps the idea of the 
metric in the sense that a perfectly league average player should have a 
PAR of 0, and his presence or 
absence from his team neither adds nor subtracts value. Thus, we have 
created a new NBA player metric, 
Points Above Replacement, PAR. All of the calculations, multiple 
regression, and graphs were created using R \citep{R}.
